### 2011-02-27 trunk/deliverables/D5_1_2/fast_d5_1_2.tex
minor changes in "planning" appendix
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@1327 d8b0c59b-6544-0410-94d9-83a5658a058e

The Catalogue is a semantic application. As a consequence, it must handle and work with ontologies and vocabularies. The business model itself is described in the FAST ontology, which is included in the Catalogue along with a few established ontologies integrated in its core (see~\cite{moeller2011fast_ontology}). However, the definition of the pre-/post-conditions of the building blocks are open to any ontology or vocabulary, and they may reference classes and properties from any of them. To have a better understanding of these classes, properties, and so on, the Catalogue needs to import into its own knowledge base the ontology in which they are described along with the relations with other classes and properties. In order to acquire these vocabularies, it follows the basic recipe dictated in~\cite{berrueta2008} which says that deferencing a vocabulary URI should provide a machine-processable (RDF) content back. Nonetheless, this is just a good practice and not every ontology published on the Internet follows it. Hence, going a step further, whenever an ontology cannot be retrieved by deferencing its URI, the Catalogue queries Sindice\footnote{http://www.sindice.com/}, a semantic search engine, which crawls and contains thousands of vocabularies and metadata as their provenance, which the Catalogue can take advantage of.

@@

Therefore, the aim of the algorithm is to find the paths or plans from a given screen to the special node or root. This is a very well-known problem in graph theory, and therefore there are many graph and tree search algorithms dealing with it, such as Floyd's, Dijkstra, A* or depth-first search, among others.

Floyd's, Dijkstra and A* are focused on finding shortest paths for a given problem. In the case of A*, the advantage is that a heuristic function may be define to prioritise a set of screens (i.e. screens in the current canvas). However, finding the shortest path is not the intention of this algorithm. In fact, it is preferred to find a small set of possible solutions, thus depth-first search is a good fit as it finds all the paths from a given node to another, avoiding cycles. Then, the paths returned by depth-first are then ranked in order to minimise the path lenght, and to maximise the number of co-occurrences of elements in the path and the canvas.

The depth-first search algorithm has not been re-implemented for the catalogue. Instead, it relies on Neo4j\footnote{http://neo4j.org/}, a flexible graph database, which apart from providing the aforesaid algorithm, it provides the necessary mechanism to store, access and query the graph. The advantages of using Neo4j are that it is highly optimized for storing graph structures for maximum performance and scalability, and supports several search algorithms, including as well Dijkstra and A*, which provides a great flexibility to the catalogue.

>>>>

The Catalogue is a semantic application. As a consequence, it must handle and work with ontologies and vocabularies. The business model itself is described in the FAST ontology, which is included in the catalogue along with a few other established ontologies (see~\cite{moeller2011fast_ontology}). However, the definition of the pre-/post-conditions of the building blocks are open to any ontology or vocabulary, and they may reference classes and properties from any of them. To have a better understanding of these classes, properties, and so on, the Catalogue needs to import into its own knowledge base the ontology in which they are described along with the relations with other classes and properties. In order to acquire these vocabularies, it follows the basic recipe dictated in~\cite{berrueta2008} which says that deferencing a vocabulary URI should provide a machine-processable (RDF) content back. Nonetheless, this is just a good practice and not every ontology published on the Internet follows it. Hence, going a step further, whenever an ontology cannot be retrieved by deferencing its URI, the Catalogue queries Sindice\footnote{http://www.sindice.com/}, a semantic search engine, which crawls and contains thousands of vocabularies and metadata as their provenance, which the Catalogue can take advantage of.

@@

Therefore, the aim of the algorithm is to find the paths or plans from a given screen to the special node or root. This is a very well-known problem in graph theory, and therefore there are many graph and tree search algorithms dealing with it, such as Floyd's, Dijkstra, A* or breadth-first search, among others.

Floyd's, Dijkstra and A* are focused on finding shortest paths for a given problem. In the case of A*, the advantage is that a heuristic function may be define to prioritise a set of screens (i.e. screens in the current canvas). However, finding the shortest path is not the intention of this algorithm. In fact, it is preferred to find a small set of possible solutions, thus breadth-first search is a good fit as it finds all the paths from a given node to another, avoiding cycles. Then, the paths returned by breadth-first are then ranked in order to minimise the path lenght, and to maximise the number of co-occurrences of elements in the path and the canvas.

The graph is updated any time a screen is created, updated or deleted in order to reflect the creation/deletion of nodes and their relationships. It is stored in the triple store where the building blocks metadata and other information is stored as well, and an implementation of the breadth-first search algorithm has been created for searching the paths or plans.

Besides, the Catalogue has been integrated with Neo4j\footnote{http://neo4j.org/}, a flexible graph database, which provides the necessary mechanisms to store, access and query the graph. Neo4j provides different graph search algorithms, including breadth-first search. The advantages of using Neo4j are that it is highly optimized for storing graph structures maximising performance and scalability, and supports several search algorithms, including as well Dijkstra and A*, which provides a great flexibility to the catalogue in case other algorithms may be needed.
